Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\extraspacing {\underline{\em Example 5.1.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type2:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$, $R_2 = \set{\beta_2, \beta_2, \beta_3}$, $H$ $=$ $\set{h_1,$ $h_2,$ $h_3}$, and $V = \set{v_1, v_2}$. The set $\J_2$ contains the following tuples: $(\alpha, \beta_1, h_2, v_1)$, $(\alpha, \beta_1, h_3, v_1)$, $(\alpha, \beta_2, h_3, v_1)$, $(\alpha, \beta_3, h_3, v_1)$, and $(\alpha, \beta_3, h_3, v_2)$. \done

>>>>

\extraspacing {\underline{\em Example 5.1.}} To illustrate our algorithm, we will utilize the running example in Figure~\ref{fig:hv:type2:ex}a, where $k = 4$, and $R_1 = \set{\alpha}$, $R_2 = \set{\beta_1, \beta_2, \beta_3}$, $H$ $=$ $\set{h_1,$ $h_2,$ $h_3}$, and $V = \set{v_1, v_2}$. The set $\J_2$ contains the following tuples: $(\alpha, \beta_1, h_2, v_1)$, $(\alpha, \beta_1, h_3, v_1)$, $(\alpha, \beta_2, h_3, v_1)$, $(\alpha, \beta_3, h_3, v_1)$, and $(\alpha, \beta_3, h_3, v_2)$. \done
